---
title: "Using the msand Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the msand Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.width=8, 
  fig.height=6
)
```

## Function Summary

The msand functions:

- `theme_msand()`: A custom theme for visualizations.
- `palette_msand()`: A personal colour palette for categorical visualizations.
- `scale_colour_msand()` & `scale_color_msand()`: For use when colour is specified as an aes() in a ggplot.
- `scale_fill_msand()`: For use when fill is specified as an aes() in a ggplot.

```{r setup}
library(msand)
```

## The Custom Colour Palette I use, `palette_msand()`.

```{r}
scales::show_col(palette_msand())
```

## The use of `theme_msand()` and `scale_colour_msand()` Example.

```{r}
library(tidyverse)

mtcars %>%
    mutate(am = ifelse(am == 0, "Automatic", "Manual")) %>% 
    ggplot(aes(hp, mpg, colour = am)) +
    geom_point(size = 2.5, alpha = 0.8) +
    scale_colour_msand() +
    theme_msand() +
    labs(title = "Miles Per Gallon vs Horse Power Coloured by Transmission Type",
         x = "Miles Per Gallon",
         y = "Horse Power",
         colour = "Transmission Type")
```

## The use of `theme_msand()` and `scale_fill_msand()` Example.

```{r}
Titanic %>% 
    as_tibble() %>% 
    uncount(n) %>% 
    ggplot(aes(Sex, fill = Survived)) +
    geom_bar(position = "fill") +
    scale_fill_msand() +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_msand() +
    labs(title = "Percent Survived vs Gender",
         x = "Gender",
         y = "Percent")
```

